\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T21:23:04+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

\textbf{(A)} If by \enquote{model} we mean a family of probability
distributions, \eg\ (apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must therefore be redefined as a family of distributions
\emph{and} a pre-data distribution over such family. This redefinition has
several consequences:

First, two models are different if they have the same family but different
distributions over it. In fact they lead to different probabilities on the
data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant, from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those
\citep[\eg][]{copasetal1979,lindleyetal1982} who find such definitions
ultimately arbitrary. Many such distributions lead, moreover, to
mathematical singularities.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T22:02:36+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

\textbf{(A)} If by \enquote{model} we mean a family of probability
distributions, \eg\ (apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in \RR_{>0}}\;,\]
then model comparison is ill-defined. % Each distribution in the family
% assigns a different probability, and it is not clear which should be
% chosen or how they should be combined and why.
It may happen that the optimal distribution in family $\mathcal{F}_{1}$
assigns more probability to the observed data than the optimal distribution
in family $\mathcal{F}_{2}$, and yet $\mathcal{F}_{1}$ assigns \enquote{on
  average} lower probabilities to the data than $\mathcal{F}_{2}$. It is
not clear how the two families should be compared in this case, or what
$\p(D \| \mathcal{F}_{i})$ is. A hypothesis is ill-defined, or at least
useless, if it does not allow us to assign a probability to the data. Such
a probability can be obtained if we specify a pre-data probability
distribution over the distributions in the family, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$ in the example above.
\enquote{Model} must therefore be redefined as a family of distributions
\emph{and} a pre-data distribution over such family
\citep{dawid1982,dawid1993}; under exchangeability, this is mathematically
equivalent to the definition (B) below
\citep[\chap~4]{bernardoetal1994_r2000}. This redefinition has several
consequences:

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different probabilities
on the data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant, from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.
